% David Snyder 2012
% resume.tex

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{#1}}%
  \item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{-0.5#1}}%
  \item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
  #1 &
  #2 \\
\end{tabular*}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{David C. Snyder}}

2718 E. 22nd St.\ \ \textbullet
\ \ Austin, TX 78722 \ \ \textbullet \ \ (512) 659-6475 
\\
davidsnyder@utexas.edu \textbullet
\ \ github.com/davidsnyder
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
  \parskip=0.1em

  \item
  \headerrow
    {\textbf{Infochimps Inc.}}
    {\textbf{Austin, Texas}}
  \\
  \headerrow
    {\emph{Software Developer}}
    {\emph{May 2010 -- January 2012}}
  \begin{itemize*}
    \item Wrote repeatable ETL workflows in Ruby as well as Apache Pig for Hadoop sized jobs. 
    \item Coded and deployed Ruby on Rails web applications in a production environment.
                \item Built a publishing pipeline with Ruby to streamline the process of uploading large datasets to HBase, ElasticSearch, and MySQL databases.
                \item Extended the Infochimps API platform to respond to additional endpoints and implemented an authentication layer with Redis. 
    \item Implemented a filesystem abstraction library for Amazon S3 and the Hadoop Distributed File System with Ruby/JRuby.
    \item Focused on repeatable deploys/systems integration with Opscode Chef on Amazon EC2 backed clusters.                  
  \end{itemize*}
\end{itemize}

\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
  \parskip=0.1em

  \item 
  \headerrow
    {\textbf{The University of Texas at Austin}}
    {\textbf{Austin, Texas}}
  \\
  \headerrow
    {\emph{College of Natural Science, B.A. Computer Science, minor Scandinavian Studies}}
    {\emph{2008 -- 2012}}
\end{itemize}

\vspace{-0.4em}
\subsection*{Projects}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{itemize*}
        \item Wrote a Clojure utility to convert WGS-84 lat/lng coordinates to quadkeys.
  \item Wrote a library of Java functions (UDFs) for Apache Pig to tile GeoJSON polygons.          
        \item Ported a Twitter tokenizer from Python to Scala as part of the University of Texas at Austin Comp. Linguistics TextGrounder project.
        \item Participated in the April 2011 3DayStartup Austin division competition and deployed a Rails group lunch voting app in under 48 hours.
        \item Rewrote the 3DayStartup voting app to be realtime with MongoDB, Websockets, Node.js, and Redis.
\end{itemize*}
\end{indentsection}

\vspace{-0.4em}
\subsection*{Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{itemize*}
        \item 2+ years experience with Ruby, Apache Pig, Hadoop
        \item Familiar with Java, C, Javascript, Clojure, Python                    
        \item Datastores: MySQL, Redis, MongoDB, HBase
        \item Web Frameworks: Ruby on Rails and Node.js      
        \item Cloud deployment and automation with Amazon EC2 and Opscode Chef
        \item Experienced with Emacs/Unix development environment
\end{itemize*}
\end{indentsection}

\end{document}
